A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-02 main.tex
linting

Section~\ref{background} defines the terminology used throughout the paper. Section~\ref{aft} outlines the training and evaluation methodology presented in this paper.  Section ~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section. Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments. Section~\ref{considerations} and Section~\ref{conclusion} reveal the caveats and the conclusions respectively.

@@

\subsection{ML Pipelines}
\label{ml_pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}. In general, a dataset is split into \textit{training} and \textit{test} sets. The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users. \cm{Since different hardware devices have differing amounts of ~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.} To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption. Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).

@@

Choosing a good learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost. A small learning rate will more accurately approximate the class boundaries~\cite{cao2019generalization}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the mini-batch size, number of epochs, dimensionality of the input data, \textit{etc.}~\cite{granziol2022learning}. GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch. A ``good'' learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}. Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment. ~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}). However, it is first necessary to define robustness.}

@@

To examine the effect of model parameters at run-time, evasion attacks, which attack the model at the prediction stage, were examined.
Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1\]$.
This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

@@

\subsection{Advantages of this Methodology}
\label{advantages}
\cm{The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements. For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe. However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:combined}).}
Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}. Furthermore, by isolating changes and testing them as quickly as possible, it is easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test. To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the IEC 61508 standard~\cite{IEC61508}, allowing the model builder to make a quantitative assessment about the efficacy of a model change without testing the effect on real users. Additionally, since AFT models have strong predictive power for untested hyper-parameter combinations, this method has a potential to reduce the search space by quickly eliminating candidates that are unlikely to increase the survival time.

@@

We have taken much care to conduct all timing measurements as carefully as possible.
Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
While it is very possible (if not altogether guaranteed) that some classes or samples are easier to attack than others, we assume that this averages out over the 100 samples given to each attack. Further work examining, for example, the effect of imbalanced datasets on the the distribution of survival times across classes is outside the scope of this work, though the methodology would remain identical. Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100). Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements. Furthermore, while \acrshort{fgm} is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
The hyper-parameter search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.

@@

~\cm{
The experiments conducted confirm that this methodology is both sound and cost-effective. While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter \acrshort{gpu}s (V100 and P100) for typical image classification tasks. Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
Figure~\ref{fig:acc} confirms the efficacy of the ~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
Additionally, Table~\ref{tab:combined} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.
}

>>>>

Section~\ref{background} defines the terminology used throughout the paper. Section~\ref{aft} outlines the training and evaluation methodology presented in this paper.  Section~\ref{cost} discusses the resulting cost analysis framework, arising from the methodology in the previous section. Section~\ref{experiments} outlines the software components and specific experiments that were conducted, while Section~\ref{results} contains the results and discussions of those experiments. Section~\ref{considerations} and Section~\ref{conclusion} reveal the caveats and the conclusions respectively.

@@

\subsection{ML Pipelines}
\label{ml_pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters.
Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}.
In general, a dataset is split into \textit{training} and \textit{test} sets. The test set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users.
\cm{Since different hardware devices have differing amounts of~\acrfull{vram}, the resulting models will have differing optimal configurations if both robustness and training cost are considered.}
To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption. Likewise, Nvidia offers hardware that is marketed as either for training (\textit{e.g.}, v100 and p100) or only for inference (\textit{e.g.}, l4).

@@

Choosing a good learning rate is critical for model performance --- greatly effecting both the accuracy and the training cost. A small learning rate will more accurately approximate the class boundaries~\cite{cao2019generalization}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the mini-batch size, number of epochs, dimensionality of the input data, \textit{etc.}~\cite{granziol2022learning}. GPUs with larger amounts of VRAM are able to hold more data in memory at a time, increasing the effective mini-batch size, and reducing the number of model-tuning steps per epoch. A ``good'' learning rate will allow a model to converge quickly~\cite{smith2019super,granziol2022learning} and the ideal mini-batch size will be determined by the memory bandwidth of the GPU and the size of the model and the size and dimensionality of the data. However, since cloud infrastructure is virtualized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}, so researchers must evaluate this \textit{in situ}. Furthermore, since hardware is typically billed by the hour on public clouds, optimising the training and inference times allows a model-builder to minimize the cost of deployment.~\cm{To optimize for training time as well as robustness (both $\lambda_{ben}$ and $\lambda_{adv}$), the \acrshort{tpe} optimization was used (see:~Section~\ref{optimisation}). However, it is first necessary to define robustness.}

@@

To examine the effect of model parameters at run-time, evasion attacks, which attack the model at the prediction stage, were examined.
Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
To evaluate the effect of adversarial noise on the samples, the noise levels were varied $0 < \varepsilon  \leq 0$.
This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

@@

\subsection{Advantages of this Methodology}
\label{advantages}
\cm{The primary advantage of this methodology over the traditional test/train split measurements is that the precision of the latter is determined by the number of samples; whereas, the precision of the survival time estimate is driven by the resolution of our timing measurements. For test-set accuracy,  meeting the weakest safety-critical IEC standard (1 failure in a million) would require many millions of samples to confidently conclude that a model is safe. However, the presented AFT model has an average error rate of 1\% while requiring a very small number of samples (10 sets of 100) (see Table~\ref{tab:aft_results}).}
Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in \acrshort{ml} applications.
This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}. Furthermore, by isolating changes and testing them as quickly as possible, it is easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test. To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the IEC 61508 standard~\cite{IEC61508}, allowing the model builder to make a quantitative assessment about the efficacy of a model change without testing the effect on real users. Additionally, since AFT models have strong predictive power for untested hyper-parameter combinations, this method has a potential to reduce the search space by quickly eliminating candidates that are unlikely to increase the survival time.

@@

We have taken much care to conduct all timing measurements as carefully as possible.
Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
While it is very possible (if not altogether guaranteed) that some classes or samples are easier to attack than others, we assume that this averages out over the 100 samples given to each attack. Further work examining, for example, the effect of imbalanced datasets on the the distribution of survival times across classes is outside the scope of this work, though the methodology would remain identical. Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100). Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements. Furthermore, while \acrshort{fgm} is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
The hyper-parameter search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.

@@

\cm{The experiments conducted confirm that this methodology is both sound and cost-effective. While 88\% of the cloud budget went to GPU rentals, the data show how cutting that cost by 75\% and using less power-intensive hardware designed for 8-bit image processing would be \textit{more} effective than using the 32-bit datacenter \acrshort{gpu}s (V100 and P100) for typical image classification tasks. Using \acrshort{kepler} proved to be a cost-effective as real-time monitoring only used a fraction of the budget (6\%).
Figure~\ref{fig:acc} confirms the efficacy of the~\acrshort{tpe} algorithm discussed in Section~\ref{optimisation}, allowing a infrastructure engineer to ignore the intricacies of learning rate optimization while tuning the model to a particular piece of hardware.
Additionally, Table~\ref{tab:aft_results} and Figure~\ref{fig:qq} show that \acrshort{aft} models are an effective way to model the survival time across hardware variants.
By comparing the training, inference, and attack  times, costs, and power consumption across different hardware devices (Figure~\ref{fig:costs}, it is clear that attacks generally cost less than training, even when we ignore the fact that attacks are consistently effective using a small number of samples while training relies on many thousands (see: Figures~\ref{fig:experiments}~\&~\ref{fig:acc}).
This analysis is further confirmed by examining the coefficients of the AFT models in Figure~\ref{fig:aft} wherein it is evident that neither training time ($T_t$) nor the number of epochs have noticeable effect on the survival time, but that model latency ($T_i$) does.}
